if(!require(psych)){install.packages("psych")}
if(!require(likert)){install.packages("likert")}



The likert package

Input =("
  Pooh    Piglet  Tigger
  3       2       4
  5       4       4
  4       2       4
  4       2       4
  4       1       5
  4       2       3
  4       3       5
  4       2       4
  5       2       4
  5       3       3
")

Data = read.table(textConnection(Input),header=TRUE)

```{r}
### Change Likert scores to factor and specify levels
Data$Pooh = factor(Data$Pooh,
                       levels = c("1", "2", "3", "4", "5"),
                       ordered = TRUE)

Data$Piglet = factor(Data$Piglet,
                       levels = c("1", "2", "3", "4", "5"),
                       ordered = TRUE)

Data$Tigger = factor(Data$Tigger,
                       levels = c("1", "2", "3", "4", "5"),
                       ordered = TRUE)

```
### Double check the data frame

library(psych)

headTail(Data)

str(Data)


'data.frame':     10 obs. of  3 variables:
 $ Pooh  : Ord.factor w/ 5 levels "1"<"2"<"3"<"4"<..: 3 5 4 4 4 4 4 4 5 5
 $ Piglet: Ord.factor w/ 5 levels "1"<"2"<"3"<"4"<..: 2 4 2 2 1 2 3 2 2 3
 $ Tigger: Ord.factor w/ 5 levels "1"<"2"<"3"<"4"<..: 4 4 4 4 5 3 5 4 4 3



summary(Data)


### Remove unnecessary objects

rm(Input)



Summary statistics and plots with the likert package
 

Percent responses in each group

```{r}
library(likert)

likert(Data)
```

    Item  1  2  3  4  5
1   Pooh  0  0 10 60 30
2 Piglet 10 60 20 10  0
3 Tigger  0  0 20 60 20

   ### Note: if there are NA’s, this summary doesn’t tell you!



### Count responses with summary function in native stats package

summary(Data)


Pooh  Piglet Tigger
 1:0   1:1    1:0   
 2:0   2:6    2:0   
 3:1   3:2    3:2   
 4:6   4:1    4:6   
 5:3   5:0    5:2

   ### Note: if there are NA’s, this summary will tell you

```{r}

library(likert)

Result = likert(Data)

summary(Result)
```

    Item low neutral high mean        sd
1   Pooh   0      10   90  4.2 0.6324555
3 Tigger   0      20   80  4.0 0.6666667
2 Piglet  70      20   10  2.3 0.8232726

   ### Note: responses are grouped into "low", "neutral", and "high"

   ### Note: if there are NA’s, this summary doesn’t tell you!



Plots that treat Likert data like factor data
 

### Bar plot

```{r}
library(likert)

Result = likert(Data)

plot(Result,
     type="bar")

```



   ### Note: for the percent numbers, 
   ###   responses are grouped into "low", "neutral", and "high"



### Heat plot
```{r}
library(likert)

Result = likert(Data)

plot(Result, 
     type="heat",
           low.color = "white", 
           high.color = "blue",
           text.color = "black", 
           text.size = 4, 
           wrap = 50)


```



Plots that treat Likert data like numeric data
 

### Density plot

```{r}
library(likert)

Result = likert(Data)

plot(Result,
     type="density",
           facet = TRUE, 
           bw = 0.5)
```


   ### Note: Vertical lines are means for each group.

   ### Note: Curves are density plots, which show the distribution of values
   ###   similar to a histogram.
