Facetting with ggplot
===========================================
Facetting
- Split into three subplots for each level of cylinder
- Each row corresponds to a level of cylinder.
```{r}
qplot(mpg, wt, data=mtcars, facets= cyl~.,
geom=c("point", "smooth"))
```
-  Three categories of cylinder : 4, 6 and 8

#### Facetting (example 2)
Using a linear regression model time
```{r}
qplot(mpg, wt, data=mtcars,
 facets=cyl~.,
 geom=c("point", "smooth"), method="lm")
```
#### Diamonds data set
```{r}
head(diamonds)
```

#### Different display of bar plots
```{r}
qplot(clarity, data=diamonds, geom="bar", fill=cut,
position="stack")
``` 
```{r} 
qplot(clarity, data=diamonds, geom="bar", fill=cut,
position="dodge")
``` 
```{r} 
qplot(clarity, data=diamonds, geom="bar", fill=cut,
position="fill")
``` 
```{r} 
qplot(clarity, data=diamonds, geom="bar", fill=cut,
position="identity")
```

1. Stack
2. Dodge
3. Fill
4. Identity 

#### Frequency Polygons
```{r}
qplot(clarity, data=diamonds, geom="freqpoly",
group=cut, colour=cut, position="identity")
``` 
```{r} 
qplot(clarity, data=diamonds, geom="freqpoly",
group=cut, colour=cut, position="stack")
```
#### Contingency table

```{r} 
table(diamonds$cut,diamonds$clarity)

``` 



More on faceting
```{r}
qplot(cty,data=Mpg2,geom="histogram",binwidth=2)
+ facet_grid(cyl ~ drv)
```
#### Margins
Faceting a plot is like creating a contingency table. It is often useful to display marginal totals as well the individual cells

#### Facet Wrap
An alternative to the grid is a wrapped ribbon of plots, `facet_wrap()` generates a long ribbon of plots, and wraps it into 2d.

#### Controlling scales
For both types of faceting you can control whether or not the position scales are the same in all panels, or allowed to vary (i.e. are the scales
“fixed” or “free”?) Fixed allows for us to compare subsets on an equal basis. It is the default setting.
Free allows us to examine each panel at the appropriate level of detail.
To specify “free” scaling, we add the phrase “scales = free” to the
`facet_grid()` or `facet_wrap()` commands.


```{r}
qplot(cty,data=Mpg2,geom="histogram",binwidth=2) +   facet_grid(cyl ~ .,scales = "free")

``` 
